Building a GNU/Hurd Cluster

### 2018-01-21 slides/cua.tex
rename 'papers' subdirectory -> 'slides'
slides - move tikz macros to a separate file

@@

\usepackage{xstring}

\usepackage{tikz}
\usetikzlibrary{positioning, fit, backgrounds, arrows, patterns, trees, shapes}

@@

\begin{frame}
\frametitle{Processor families in TOP500}
\includegraphics[width=\textwidth]{Processor_families_in_TOP500_supercomputers.png}
\end{frame}

@@

\begin{frame}
\frametitle{Intel Ivy Bridge Processor}
\includegraphics[width=\textwidth]{ivybridge.jpg}
\begin{center}
\huge
Notice the size of the graphics co-processor!
\end{center}
\end{frame}

@@

\begin{frame}
\frametitle{Cisco 5108 Blade Server Chassis with eight B200 M2s}
\includegraphics[width=\textwidth]{ourcisco.jpg}
\end{frame}

@@

\begin{frame}
\frametitle{How many Debian packages build on Hurd?}
\includegraphics[width=\textwidth]{graph-big.png}
\end{frame}

% tikz commands to draw task boxes to illustrate Mach IPC concepts

\tikzstyle{task} = [draw, fill=blue!20, rounded corners]

% \task - takes four arguments
% 1. name of task (used to refer to it from tikz; maybe printed as a label as well)
% 2. location of task box's center point
% 3. "r" or "l", indicating if a set of tick marks representing
%    ports should drawn on the left or right side of the task box
%    "u" to label the task "Task" instead of labeling it with its name
%    "b" to make a "big" node (I wish I knew how to size the tick marks automatically)
%    "s" to make a "small" node
% 4. contents of the task box - other nodes
%
% The tick marks will be named "#1 Port #" for future reference
%
% It's implemented as a tikz matrix with two cells - the task name in the top cell
% and everything else in the bottom cell

\newcommand\task[4]{
\matrix (#1) [task, inner xsep=0] at (#2) { \node {\IfSubStr{#3}{u}{Task}{#1}}; \\ #4

% print port tick marks in fill color if they are disabled, in order to make
% them expand out the dimensions of the task box yet remain invisible

\IfSubStr{#3}{b}{\edef\starti{-20}}{\IfSubStr{#3}{s}{\edef\starti{-1}}{\edef\starti{-7}}}
\IfSubStr{#3}{s}{\edef\endi{1}}{\edef\endi{7}}

\foreach \i in {\starti,...,\endi}
{
  \IfSubStr{#3}{l}{\edef\leftcolor{black}\edef\leftcoord{coordinate (#1 Port \i)}}
                  {\edef\leftcolor{blue!20}\edef\leftcoord{}}
  \IfSubStr{#3}{r}{\edef\rightcolor{black}\edef\rightcoord{coordinate (#1 Port \i)}}
                  {\edef\rightcolor{blue!20}\edef\rightcoord{}}
  \draw[xshift=-5em, ultra thick, color=\leftcolor] (0,0.2 * \i) \leftcoord -- (0.2,0.2 * \i);
  \draw[xshift=5em, ultra thick, color=\rightcolor] (-0.2,0.2 * \i) -- (0,0.2 * \i) \rightcoord;
}

\\};
}

% draw a box with vertical lines to represent a message queue
% arg 1 is the name of a port to position it to the left of
% arg 2 is name to be given the box

\newcommand\queue[2]{
\filldraw (#1) +(-3.1,0) node[rectangle, name=#2, minimum width=1.8cm, minimum height=1cm, draw, pattern=vertical lines] {};
}

@@

%\begin{frame}
%\frametitle{Example: Basic File I/O}
%\end{frame}

@@

\filldraw (-30 em, 15em) node[rectangle, name=queue 1, minimum width=1.8cm, minimum height=1cm, draw, pattern=vertical lines] {};
% \task{Task 0}{-30 em,15 em}{ur}{}

>>>>

% Slideshow, written by Brent Baccala, for a lecture at Catholic University
%
% A screencast of the original lecture is available on youtube:
%
% https://www.youtube.com/watch?v=JwsuAEF2FYE

@@

\usepackage{hurd}

\usepackage{tikz}
\usetikzlibrary{positioning, fit, backgrounds, arrows, trees, shapes}

@@

\begin{frame}
\frametitle{Processor families in TOP500}
% https://upload.wikimedia.org/wikipedia/commons/thumb/e/ef/Processor_families_in_TOP500_supercomputers.svg/800px-Processor_families_in_TOP500_supercomputers.svg.png
\includegraphics[width=\textwidth]{Processor_families_in_TOP500_supercomputers.png}
\end{frame}

@@

\begin{frame}
\frametitle{Intel Ivy Bridge Processor}
% https://www.pcper.com/files/review/2012-04-22/slides03.jpg
\includegraphics[width=\textwidth]{ivybridge.jpg}
\begin{center}
\huge
Notice the size of the graphics co-processor!
\end{center}
\end{frame}

@@

\begin{frame}
\frametitle{Cisco 5108 Blade Server Chassis with eight B200 M2s}
% https://drive.google.com/uc?export=download&id=1UVc0DbcYrSk5DNcCGneIU_RmkW83JQFA
\includegraphics[width=\textwidth]{ourcisco.jpg}
\end{frame}

@@

\begin{frame}
\frametitle{How many Debian packages build on Hurd?}
% https://buildd.debian.org/stats/graph-big.png
\includegraphics[width=\textwidth]{graph-big.png}
\end{frame}

@@

@@

\filldraw (-30 em, 15em) node[rectangle, name=queue 1, minimum width=1.8cm, minimum height=1cm, draw, pattern=vertical lines] {};
